---
title: "STAT 107 Project"
author: "Danny Espinoza Cardenas"
format: html
execute:
  echo: false
  warning: false
  message: false
editor: visual
---

## Introduction

This dataset contains 21 body dimension measurements as well as age, weight, height, and gender on 507 individuals. The 247 men and 260 women were primarily individuals in their twenties and thirties, with a scattering of older men and women, all exercising several hours a week. The original dataset contains skeletal and muscular girth measurements. For this project I will be analyzing the below muscular girth measurements as well as age, weight, height, and gender. I am omitting the skeletal data because I am unable to measure my own bone structure for the purpose of my research question.

My research question is figuring out the statistics of where my personal muscular girth measurements would place me within a 10 year range. Comparing myself to these physically active individuals, I should be on the low tail of the data since I do no workout often. I do partake in latin dancing at least an hour or two every week and I walk my dog a minimum of 30 minutes a day, but that is probably far different than active lifestyle of individuals in the original data. That is, where does a 26-year-old lightly active male place relatively to highly active young adults of age 21 - 31 in terms of weight? I also seek to discover if my weight follows the same trend when accounting for all muscular girth measurements.

```{r}
source("Data_Dictionary.R")
```

## Methods

First I will look at where I land compared to three groups, Group A: 21 - 31 year old males, Group B: 21 - 31 year old females, Group C: 21 - 31 year old females and males. This will be done by comparing my position across the 3 distributions and determine my standing through z-score and percentile rankings with Group A. For Group B and C, I will be producing a table comparing the averages as they are not my main focus group for comparison.

First, I created a table using bind_rows() and summarise() to calculate the averages across all the columns, except gender. That table exists for simple comparison between all the three groups.

I then used hist() in a for loop to graph small histograms with a red abline() showcasing where my measurements land according to the distribution of each category compared to Group A.

```{r}
source("EDA_Setup.R")
```

Next, I will check for normality before conducting my statistical inference of whether I can reject or fail to reject the hypothesis of my values being statistically lower than the average of Group A, which is the most relevant subgroup. Although visually I appear to be below the mean in most categories, I am choosing weight as an overall variable to determine if that is statistically true. This is done through a one sided t-test with hypothesis: $H_0: \mu_{\text{weight}} = 58.35$ $H_A: \mu_{\text{weight}} > 58.35$

Finally, I will check all categories through a multivariate linear regression model to analyze if all the muscular girths to predict weight can determine if my weight truly is truly different than the trend of active individuals.

## Results

```{r}
source("T-Test.R")
```

A p-value \< 2.2e-16 at $\alpha = 0.05$ determines that we can reject the null hypothesis. That is, the mean weight of Group A is not 58.35 kg, but rather much higher around `r round(mean(group_males$weight, na.rm = TRUE), 2)` kg.

So I am statistically far below the mean—specifically, `r round(my_z_score, 3)` standard deviations away from the mean weight of active males between ages 21–31. This places me in the bottom `r round(pnorm(my_z_score) * 100, 2)`% compared to the active males of Group A.

```{r}
source("Multivariate_Regression.R")
```

There is `r round(summary(multivariate_model)$adj.r.squared, 3)` variability accounted for by the 12 girth measurements, so this model should be a good prediction model for the weight of active males.

Looking at my blue data point, I follow the trendline and so although I was statistically below the average for weight, when I account for all variables I am actually inline with the group of active individuals.

Looking at the residual plot, my predicted weight should lie on the red trendline, but I am slightly below which means \*\*my actual weight of `r my_row$weight` kg is less than the model's prediction of `r round(my_predicted_weight, 2)` kg . This results in a negative residual of `r round(my_residual, 2)`. This could suggest that relative to the active males, I have a lower mass density, either muscle or the unmeasured bone / skeletal density, than an average active male with my specific frame size and muscular girths.

## Discussion

Overall, I found that while I was below the mean in all stats of muscular girth, I am actually not too different when comparing my weight compared to my overall girth measurements. Although I am slightly below, my results show that with a bit of exercise I have the ability to reach those same girths. The skeletal density due to having a smaller frame is an interesting component that I would love to get professionally measured. Which leads me to the one thing that I would do differently is get my measurements done professionally rather than using a simple tape measure and weight scale. My results are very interesting because I had always considered myself to be "skinny fat" but statistically showing that i am actually not too far off from what is deemed average is fascinating.

## Appendix
